abc

### 2024-10-06 randpython.qmd
test

@@

    allrot = [ps[i] for i in sel]
    return allrot
```

```{pyodide-python}
def genpolycoeffn(form,expr,solv):
    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
    x, y, z = sympy.symbols('x y z')
    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
    parm = elem[2-1][:5]
    ls, rs = expr.split('=')
    expr = Eq(sympify(ls), sympify(rs))
    plr = int(sympy.total_degree(expr))-1
    polys = poly(expr.rhs - expr.lhs, sympify(solv)).all_coeffs()
    abc = [1,0,0,0,1,0,0,0,1]
    uvw = []
    ABCDE = [0, 0, 0, 0, 0]
    ABCDE[:len(polys)] = polys
    matarch = 0
    return ABCDE, abc, matarch, plr

```

```{pyodide-python}

@@

@@

```

```{pyodide-python}
testn = genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
```

```{pyodide-python}
testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha')
```

```{r, echo=F, eval=T}
knitr::knit_exit()
```

>>>>

```{pyodide-python}
import sympy, pandas, numpy, math
```

@@

    allrot = [ps[i] for i in sel]
    return allrot

def genpolycoeffn(form,expr,solv):
    forp = {'N': 1, 'H': 2, 'O': 3}
    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
    x, y, z = sympy.symbols('x y z')
    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
    parm = elem[2-1][:5]
    ls, rs = expr.split('=')
    expr = Eq(sympify(ls), sympify(rs))
    plr = int(sympy.total_degree(expr))-1
    polys = poly(expr.rhs - expr.lhs, sympify(solv)).all_coeffs()
    abc = [1,0,0,0,1,0,0,0,1]
    uvw = []
    ABCDE = [0, 0, 0, 0, 0]
    ABCDE[:len(polys)] = polys
    matarch = 0
    return ABCDE, abc, matarch, plr

#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')

@@

    #breakpoint()

@@

genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',[1,2,4])[2]

def pareq(ste='(x + y*zeta)/(zeta + 1)', **kwargs):
    return eval(ste, kwargs)

prv = ["g","h","alpha"]
rve = [1, 2, 4]
gra = [-44.9573,7.001545,-19.9677]
eqs = ["z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3","alpha=k0+k1*g+k2*h+k3*Gamma"][0]
sfo = ['g','h','alpha'][2]
test = genpolycoeffr(elem=prv,expr=eqs,solv=sfo,eur=rve)
m1v = math.cos(math.radians(gra[0]))
m2v = math.cos(math.radians(gra[1]))
m3v = math.cos(math.radians(gra[2]))
n1v = math.sin(math.radians(gra[0]))
n2v = math.sin(math.radians(gra[1]))
n3v = math.sin(math.radians(gra[2]))
m1v, m2v, m3v, n1v, n2v, n3v
k0=0.001643394  
k1=1.075717880 
k2=-0.731335532
k3=0.064912642  
k4=0.064007760 
k5=-0.785443920
k6=0.092375583 
k7=-1.271709722  
k8=3.038048882
k9=0.923841730

# I
a1 = pareq(ste=str(test[1][0]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
a2 = pareq(ste=str(test[1][1]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
a3 = pareq(ste=str(test[1][2]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
b1 = pareq(ste=str(test[1][3]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
b2 = pareq(ste=str(test[1][4]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
b3 = pareq(ste=str(test[1][5]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
c1 = pareq(ste=str(test[1][6]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
c2 = pareq(ste=str(test[1][7]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
c3 = pareq(ste=str(test[1][8]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)

results = []
for nr in range(20):  # Example: looping from 0 to 19, you can change the range as needed
    lhs = test[2]['d'][nr]
    rhs = test[2]['expr'][nr]
    pareq_result = plsv.pareq(
        str(rhs),
        a1=a1, a2=a2, a3=a3,
        b1=b1, b2=b2, b3=b3,
        c1=c1, c2=c2, c3=c3,
        k0=k0, k1=k1, k2=k2, k3=k3, k4=k4, k5=k5, k6=k6, k7=k7, k8=k8, k9=k9
    )
    # Append the result dictionary directly to the list
    results.append({
        'lhs': lhs,
        'rhs': rhs,
        'pareq_result': pareq_result
    })

df_results = pd.DataFrame(results)
```

```{pyodide-python}
a1, a2, a3, b1, b2, b3, c1, c2, c3
```

```{pyodide-python}
# https://docs.google.com/spreadsheets/d/1Qf51QlYkCmd8h72R5JrFUt9VYCgpq8U_RyQTLzOoiFc/edit?gid=499474525#gid=499474525
df_results 
```
